\chapter{Glossary}
%TODO añadir terminos importantes o abstractos (no solamente siglas)
	%payload
	%signature
%dar por hecho cosas como AES, TLS, PMBOK, PMI ?
%quitar del texto normal las explicaciones ?
	%done="$(awk -F '{' '/\\textbf\{/ {print $2}' glossary.tex  |cut -d '}' -f1 |tr '\n' '|')"; \grep -E '\b[[:upper:]][[:upper:]]+\b'  *.tex |cut -d ':' -f2  | \grep -v '^[[:space:]]*%' |\grep -Eo '\b[[:upper:]][[:upper:]]+\b' | sort -u |grep -vE "UNIVERSITY|SANTIAGO|COMPOSTELA|ESCOLA|TÉCNICA|SUPERIOR|DE|ENXEÑARÍA|TODO|LARGE|STATE|JSON|XML|FAQ|UDP|TCP|IP|ARD|CA|CRD|GNU|GPL|OF|PA|RD|SL|TF|SEC|WBS|KERB|REQUEST|CPU|DIT|HOST|NTDS|OR|PS|RAM|RNF|RNO|RYES|SYSTEM|UNKNOWN|WIN|WMIC|${done:0:-1}"


\textbf{AD}: Active Directory. The directory domain of Windows systems, thought it can be also used by GNU/Linux with Samba.
\linej
\linej
\textbf{API}: Application Program Interface. Is a set of subroutines, functions and procedures from a library to be used by other software.
\linej
\linej
\textbf{AWK}: Programming language created by Alfred \textbf{A}ho, Peter \textbf{W}einberger, and Brian \textbf{K}ernighan, used mostly for string parsing.
\linej
\linej
\textbf{AES}: Advanced Encryption Standard. Popular symmetric encryption algorithm with different key lengths.
\linej
\linej
\textbf{CDB}: Short for constant database. File format and library for item creation and reading in a database at fast speeds.
\linej
\linej
\textbf{DC}: Domain Controller. In this case a server that runs part of an Active Directory domain. The main DC is named Primary Domain Controller.
\linej
\linej
\textbf{DLL}: A Dynamic Link Library file. It is a grouping of code or data for programs of the system. It is in a separate file for easier management or better performance.
\linej
\linej
\textbf{ELK}: Elasticsearch, Logstash and Kibana. Stack used for Wazuh to gather and transform data.
\linej
\linej
\textbf{Golden Ticket}: Forged TGT that normally provides access as administrator of the AD for 10 years.
\linej
\linej
\textbf{GPDR}: General Data Protection Regulation. Regulation in EU law on data protection and privacy for all individuals within the European Union and the European Economic Area. In practice in this project means law protected files against changes.
\linej
\linej
\textbf{HIDS}: Host-based Intrusion Detection System.
\linej
\linej
\textbf{ICS}: Industrial Control System. They are control systems for critical tasks. Normally they are used for industrial control, but in this project we consider any purpose, like data analysis.
\linej
\linej
\textbf{IDS}: Intrusion Detection System. Mitigates the damage of intrusions, providing passive protection by alerts.
\linej
\linej
\textbf{IPS}: Intrusion Prevention System. Minimizes the chance of intrusions, providing active protection by actions.
\linej
\linej
\textbf{KDC}: Key Distribution Center. Service that handles the Kerberos requests. It runs in a DC.
\linej
\linej
\textbf{Kerberos}: Computer network authentication protocol that uses tickets to allow computers over a network to authenticate in a secure manner. Windows 2000 and later uses Kerberos as its default authentication method.
\linej
\linej
\textbf{KRBTGT}: Kerberos super-administrator account, used for encrypting all the authentication tokens for the DC. Is hidden, local, can not be deleted, neither the name changed.
\linej
\linej
%\textbf{PMBOK}: Project Management Body of Knowledge. Is a set of standard terminology and guidelines for project management.
%\linej
%\linej
%\textbf{PMI}: Project Management Institute. Nonprofit proffesional organization for project management.
%\linej
%\linej
\textbf{Metasploit}: Penetration testing framework. There are Windows and GNU/Linux versions.
\linej
\linej
\textbf{Meterpreter}: Meterpreter is a Metasploit attack payload that provides an interactive shell from which an attacker can explore the target machine and execute code. Meterpreter is deployed using in-memory DLL injection.
\linej
\linej
\textbf{Mimikatz}: Program to extract authentication data or generate forged authentication tickets. In this project we use it for extracting the KRBTGT hash and generating Golden Tickets.
\linej
\linej
\textbf{LSA}: Short for \textbf{L}ocal \textbf{S}ecurity \textbf{A}uthority Subsystem Service. Process in Microsoft Windows operating systems that is responsible for enforcing the security policy on the system. It verifies users logging on to a Windows computer or server, handles password changes, and creates access tokens.
\linej
\linej
\textbf{LSASS}: Local Security Authority Subsystem Service. Process in Microsoft Windows operating systems that is responsible for enforcing the security policy on the system. It verifies users logging on to a Windows computer or server, handles password changes, and creates access tokens.
\linej
\linej
\textbf{NIDS}: Network-based Intrusion Detection System.
\linej
\linej
\textbf{OSSEC}: \textbf{O}pen \textbf{S}ource HIDS \textbf{SEC}urity. Is an HIDS solution with detection based on rules and decoders.
\linej
\linej
\textbf{OU}: Organizational Unit. They are a type of group structure for AD.
\linej
\linej
\textbf{Samba}: Is a set of programs for interoperability between Linux and Windows.
\linej
\linej
\textbf{SMB}: Server Message Block protocol for sharing files, printers, communications, etc in Microsoft systems. Some of its services can be accessed with Samba.
\linej
\linej
\textbf{Shadow Copy}: Windows technology for copying files or volumes when they are in use.
\linej
\linej
\textbf{SID}: Security Identifier. Unique value used to differentiate security elements or groups in Windows Systems.
\linej
\linej
\textbf{TGT}: Ticket Granting Ticket. This ticket is encrypted with the KDC key and is used for request to the KDC one or more TGS.
\linej
\linej
\textbf{TGS}: Ticket Granting Service. This ticket is encrypted with the service key and is used to authenticate against a service.
\linej
\linej
\textbf{TLS}: Transport Layer Security. Cryptography protocol designed to provide communications security over a computer network with hybrid (symmetric and asymmetric) cryptography.
\linej
\linej
\textbf{YARA}: Tool that does pattern/string/signature matching, with great in performance, results and easiness to write rules.
\linej
\linej
